---
title: "Practical Machine Learning Project"
author: "Zucethy Obando"
date: "11/20/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
##Project Introduction
The goal of your project is to predict the manner in which they did the exercise. This is the "classe" variable in the training set. You may use any of the other variables to predict with. You should create a report describing how you built your model, how you used cross validation, what you think the expected out of sample error is, and why you made the choices you did. You will also use your prediction model to predict 20 different test cases.


##Load libraries

```{r}
library(caret)
library(dbplyr)
library(rpart.plot)
```

##Data Processing

###Load Data
```{r}
plm_training <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"), na.strings=c("NA","#DIV/0!",""))
plm_test <- read.csv(url("https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"), na.strings=c("NA","#DIV/0!",""))
```

###Data Cleasing
```{r}
plm_training = plm_training[, colSums(is.na(plm_training)) == 0]
plm_test = plm_test[, colSums(is.na(plm_test)) == 0]
```

Remove 7 first columns because they have high cardinality and aren't good features
```{r}
plm_training = plm_training[, -c(1:7)]
plm_test = plm_test[, -c(1:7)]
```

###Create training set and test set
```{r}
set.seed(998)
trCtrl = trainControl(method = 'repeatedcv', number = 2, repeats = 2)
index = createDataPartition(plm_training$classe, p = 0.6, list = FALSE) 
train = plm_training[index, ]
test = plm_training[-index, ]
```

###Create a Random Forest to improve Decision Tree accuracy
```{r}
dc_model <- train(classe ~ ., data=train, method="rf", trControl=trCtrl)
dc_model
```

###Predict target
```{r}
y_predicted = predict(dc_model, newdata= test)
```

###Validate predicted values
```{r}
confusionMatrix(test$classe, y_predicted)
```

###Conclusion
The random forest algorithm is given a good accuracy and can be used to predict classe on test set
```{r}
classe_predict = predict(dc_model, newdata = plm_test)
classe_predict
```